Measuring Software Ticket Quality using Quantitative Data Analysis

### 2018-04-19 paper/paper.tex
Add acknowledgements section on paper

A Welch T Test was computed to test the difference between tickets with attachments and those 
without attachments. The analysis revealed significant difference with \emph{p} < 0.01 with an
average of \emph{X <change this>} for tickets with attachments and an average of \emph{Y <change this>}
for tickets without attachments.

@@

@@

\vskip8pt \noindent
{\bf Acknowledgments.}
Tim, my parents, Corina.

>>>>

Stack traces are active stack frames at a certain point in time while the program is executing. 
Many programming languages provide stack traces through their standard libraries, but the most 
popular proponents are Java and C\#. As Java is the main programming language used throughout 
the Apache Software Foundation projects (231 projects \cite{apache_projects}), many of the projects 
we collected (22) are also written in Java, thus we had a considerable chunk of data to analyze.

For this analysis, we only looked at tickets of high priority, closed and the project they correspond 
is written in Java. We then ran a complex regular expression derived from the works of Bettenburg et. al 
\cite{bettenburg2012using} and Moreno et. al \cite{moreno2014use} and collected all the tickets that have 
stack traces. In the end, we got a total number of 256 tickets that had at least an exception stack trace 
attached in either summary, description or any of the comments.

As shown in Figure \ref{stack_traces}, we can see that the presence of exception stack traces can 
reduce the time-to-close of a ticket in orders of magnitude. This could imply that stack traces help 
developers working on the project localise the code that is running exceptions

We computed a Welch T Test to test the difference between tickets with stack traces and tickets that 
do not have stack traces. The analysis revealed significant difference with $p < 0.01$ with an
average of $1475.074$ for tickets with stack traces and an average of $2441.877$
for tickets without them.

@@

The first extension to the Go tool we created would be to add support for Bugzilla as an issue tracking system

@@

\vskip8pt \noindent
{\bf Acknowledgments.}
I would first like to thank Dr. Storer for the amazing work he has put in helping me go through with finishing 
this project. I would definitely not have been able to achieve what we've achieved with any other supervisor, so 
thank you, Tim, for all the support, kindness and advice you have given me throughout this academic year. I would 
also like to thank you for being the lecturer who has taught me the most throughout all my years at the university
and whose advice and ideas I have applied at all my work places and my personal projects.
The next huge thank you would have to go to my parents, the most amazing family in the world! Without them I would 
not be here and I wouldn't have had anything of what I have now, both personally and professionally. 
I will always treasure the unconditional support you have always offered me! Thank you for being my parents, Mom and Dad!
And last but not least, I want to thank my partner in \"crime\" and in life, Corina! Without her, I would not be who I 
am today. You have been with me through thick and thin, in both bad moments (such as the endless nights working 
on ticket statistics) and best moments in my life! Thank you for everything! I will always love you!
